---
title: "Basic usage of TraceQC"
output: 
  html_document:
    toc: true
    toc_float: true
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_chunk$set(message = FALSE)
library(TraceQC)
library(fastqcr)
data(example_obj)
``` 

## Data

The example object is generated using a FASTQ file that contains randomly sampled 5,000 reads from Church's data. # We need to have a citation!

A TraceQC object has five different elements, as it is seen in the following output.

```{r}
summary(example_obj)
```


## Plot construct
```{r construct}
plot_construct(example_obj)
```

## FastQC {.tabset}

### Per base quality
``` {r}
qc_plot(example_obj$qc, "Per base sequence quality")
```

### Per sequence quality
``` {r}
qc_plot(example_obj$qc, "Per sequence quality scores")
```

### Sequence length distribution
``` {r}
qc_plot(example_obj$qc, "Per base N content")
```

## Score distribution
``` {r score}
plot_score_distribution(example_obj)
```

## Lorenz curve
``` {r lorenz}
lorenz_curve(example_obj)
```


## Number of mutations per barcode
``` {r}
num_mutation_histogram(example_obj)
```

## Mutation types
``` {r,message=FALSE}
mutation_type(example_obj)
```

## Mutation Hotspot {.tabset}

### Deletions
``` {r}
plot_deletion_hotspot(example_obj)
```

### Insertions
``` {r}
plot_insertion_hotspot(example_obj)
```

### Mutations
``` {r}
plot_point_mutation_hotspot(example_obj)
```
