---
title: "Creating a TraceQC object"
output: html_document
---

Three different files are required to create a TraceQC object.

```{r}
library(TraceQC)
```

* `input_file`: It is a FASTQ file from an experiment of linage tracing experiment using CRISPR.

```{r}
input_file <- system.file("extdata", "test_data",
                          "fastq", "example.fastq", package="TraceQC")
cat(readLines(input_file)[1:4], sep = "\n")
```

* `ref_file`: It is a text file that contains a construct (for reference) sequence.


```{r}
ref_file <- system.file("extdata", "test_data", "ref",
                        "ref.txt", package="TraceQC")
cat(readLines(ref_file), sep = "\n")
```

* `input_qc_path`: A path to the [FastQC](https://www.bioinformatics.babraham.ac.uk/projects/fastqc/) file which is corresponded to `input_file`. It is possible to execute or bring the FastQC file outside the workspace, but if there has been no FastQC file yet, then it is possible to create it using `fastqcr` package. The package can be installed by using `install_external_packages`. To generate a FastQC file and get the path, the following lines are needed.

```{r}
qc_dir <- tempdir() # It is possible to set the dir to another location.

# The first argument is a directory, not a path, 
# so if there are multiple FASTQ files in a directory, it doesn't have to run
# `fastqc` function multiple times.
fastqc(system.file("extdata", "test_data",
                   "fastq", package = "TraceQC"), 
       qc.dir=qc_dir)
# This function tell where the FastQC file which is corresponded to `input_file`.
input_qc_path <- get_qcpath(input_file, qc_dir)
```

After the required files are ready, running `TraceQC` will generate an object.

```{r}
obj <- TraceQC(input_file = input_file,
               ref_file = ref_file,
               fastqc_file = input_qc_path)
```
