---
title: "TraceQC Application"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{TraceQC Application}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

`TraceQC` is a versatile tool. In addition to performing Quality Control, it can be used to run additional analysis such as phylogenetic reconstruction. This document shows how to load the object to run a phylogenetic reconstruction using the `phangorn` and `ggtree` package.

First, we load the `TraceQC` package and an example object (`example_obj`).

```{r setup}
library(TraceQC)
library(phangorn)
library(ggtree)
library(cowplot)
library(magrittr)
data(example_obj)
```

Next, `build_binary_table` in `TraceQC` will convert the object to a list that contains a matrix (`binary_table'), sequence information (`seq_id'), and .

```{r, message=FALSE}
tree_input <- build_binary_table(example_obj)
summary(tree_input)
```


Finally, we can reconstruct a phylogenetic tree with the following code:

``` {r figure.width=8, figure.height=16}
phyDat_obj <- table_to_phyDat(tree_input)
plot_phylogenetic_tree(phyDat_obj)

````
