---
title: "CRISPR Lineage Tracing QC"
output: 
  html_document:
    toc: true
    toc_float: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_chunk$set(message = FALSE)
library(dplyr)
library(tidyr)
library(magrittr)
library(knitr)
library(kableExtra)
library(readr)
library(stringr)
library(ggplot2)
library(stringr)
library(fastqcr)
library(TraceQC)
library(RColorBrewer)
library(circlize) # Added due to a function dependency, has to be out 
library(ComplexHeatmap) # Added due to a function dependency, has to be out 
``` 

## Data
Randomly sampled 5000 reads from Church's data.

## Plot construct
```{r construct}
ref <- system.file("extdata", "test_data","ref.txt",package = "TraceQC")
plot_construct(ref)
```

## FastQC {.tabset}
```{r QC}
qc_dir <- tempdir()
testdata_path <- system.file("extdata", "test_data",package = "TraceQC")
fastqc(testdata_path,qc.dir=qc_dir)
```

### Per base quality
``` {r}
qc <- qc_read(file.path(qc_dir, "example_fastqc.zip"))
qc_plot(qc, "Per base sequence quality")
```

### Per sequence quality
``` {r}
qc_plot(qc, "Per sequence quality scores")
```

### Sequence length distribution
``` {r}
qc_plot(qc, "Per base N content")
```

## Alignment
``` {r align}
library(reticulate)
# use_miniconda()
# py_install("pandas")
# py_install("numpy")
# py_install("biopython")

start_time <- Sys.time()
align_script <- system.file("py", "alignment.py", package="TraceQC")
input_file <- system.file("extdata", "test_data", "example.fastq", package="TraceQC")
ref_file <- system.file("extdata", "test_data", "ref.txt", package="TraceQC")
output_file <- tempfile()

source_python(align_script)

args <- list("input"=input_file,
          "reference"=ref,
          "output"=output_file,
          "match"=2,"mismatch"=-2,"gapopen"=-6,
          "gapextension"=-0.1)
alignment(r_to_py(args))

end_time <- Sys.time()
paste("Aligning 5000 reads in", round(end_time - start_time,2))
```

## Output file
``` {r out}
aligned_reads <- read_tsv(output_file)
kable(head(aligned_reads) %>% select(name,score)) %>%
  kable_styling(bootstrap_options = "striped", full_width = F)
```

## Score distribution
``` {r score}
plot_score_distribution(aligned_reads)
```

## Lorenz curve
``` {r lorenz}
lorenz_curve(aligned_reads)
```

## Sequence to character
``` {r s2c}
start_time <- Sys.time()
output_seq_to_char <- tempfile()
mutation_df <- seq_to_character(aligned_reads, output_seq_to_char)
kable(head(mutation_df) %>% select(count,type,start,length))
end_time <- Sys.time()
paste("It takes",end_time-start_time)
```

## Number of mutations per barcode
``` {r}
num_mutation_histogram(mutation_df)
```

## Mutation types
``` {r,message=FALSE}
mutation_type(mutation_df)
```

## Mutation Hotspot {.tabset}

### Deletions
``` {r}
plot_deletion_hotspot(mutation_df,ref)
```

### Insertions
``` {r}
plot_insertion_hotspot(mutation_df,ref)
```

### Mutations
``` {r}
plot_point_mutation_hotspot(mutation_df,ref)
```

## Mutation rate
``` {r}
args <- list("input"=system.file("extdata", "test_data", "example_0d.fastq", package = "TraceQC"),
          "reference"=system.file("extdata", "test_data", "ref.txt", package = "TraceQC"),
          "output"= tempfile(),
          "match"=2,"mismatch"=-2,"gapopen"=-6,
          "gapextension"=-0.1)
alignment(args)
aligned_reads <- read_tsv(args$output)

output_0d <- tempfile()
seq_to_character(aligned_reads,output_0d)

args <- list("input"=system.file("extdata", "test_data", "example_2d.fastq", package = "TraceQC"),
          "reference"=system.file("extdata", "test_data", "ref.txt", package = "TraceQC"),
          "output"= tempfile(),
          "match"=2,"mismatch"=-2,"gapopen"=-6,
          "gapextension"=-0.1)
alignment(args)
aligned_reads <- read_tsv(args$output)

output_2d <- tempfile()
seq_to_character(aligned_reads,output_2d)


args <- list("input"=system.file("extdata", "test_data", "example_14d.fastq", package = "TraceQC"),
          "reference"=system.file("extdata", "test_data", "ref.txt", package = "TraceQC"),
          "output"= tempfile(),
          "match"=2,"mismatch"=-2,"gapopen"=-6,
          "gapextension"=-0.1)
alignment(args)
aligned_reads <- read_tsv(args$output)

output_14d <- tempfile()
seq_to_character(aligned_reads,output_14d)


data <- list("day0"=read_tsv(output_0d),
             "day2"=read_tsv(output_2d),
             "day14"=read_tsv(output_14d))

merged_df <- data.frame()
for (d in names(data)) {
  tmp <- select(data[[d]],-target_seq) %>%
      group_by(type,start,length,mutate_to) %>%
      summarise(count=sum(count)) %>%
      ungroup
  names(tmp)[names(tmp)=="count"] <- d
  
  if (nrow(merged_df)==0) {
    merged_df <- tmp
  }
  else {
  merged_df <- full_join(merged_df,tmp,by=c("type","start","length","mutate_to"))}
}

unmutated_count <- filter(merged_df,type=="unmutated") %>%
  select(names(data)) %>%
  gather(day,unmutated_count) %>%
  mutate(day=factor(day,levels=c("day0","day2","day14")))

unmutated_count$tot_count <- 5000

ggplot(unmutated_count,aes(x=day,y=1-unmutated_count/tot_count)) +
  geom_point(size=5) +
  geom_path() +
  ylab("mutated percentage") +
  theme_classic()
```


## Build phylo tree
``` {r}
library(phangorn)
library(ggtree)

data <- build_character_table(mutation_df)
print(data[1:10,1:10])
data <- phyDat(data=data,type="USER",levels=c(0,1))
dm <- dist.hamming(data)
treeUPGMA <- upgma(dm)
treePars <- optim.parsimony(treeUPGMA, data)
ggtree(treePars) + geom_tiplab()
```

