---
output: 
  html_document:
    toc: true
    toc_float: true

params:
  date: !r Sys.Date()
  set_title: "TraceQC report"
  debug: TRUE
  traceQC_obj: !r NULL
  input_file: !r system.file("extdata", "test_data", "FASTQ", "example_small.fastq.gz", package="TraceQC")
  ref_file: !r system.file("extdata", "test_data", "ref", "ref.txt", package="TraceQC")
  fastqc_dir: !r tempdir()
  rds_path: !r tempfile(fileext=".rds")
  alignment_score_threshold: !r NULL
  ncores: 1
---

---
title: `r params$set_title`
date: `r params$date`
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(TraceQC)
library(fastqcr)
library(tictoc)
library(knitr)
library(dplyr)
library(magrittr)
library(kableExtra)
```


```{r data_loading, include=FALSE, warning=FALSE, include=FALSE}
tic("Running time to create the report")
if(!params$debug) {
  if(is.null(params$traceQC_obj)) {
      fastqc(dirname(params$input_file), qc.dir=params$fastqc_dir)
      fastqc_file <- get_qcpath(params$input_file, params$fastqc_dir)
      cur_obj <- TraceQC(
        input_file = params$input_file,
        ref_file = params$ref_file,
        fastqc_file = fastqc_file,
        ncores = params$ncores)
  }
  else {
   cur_obj <- readRDS(params$traceQC_obj)
  }
} else {
  data(example_obj)
  cur_obj <- example_obj
}
```

## Input files to generate the report

* Input file: `r params$input_file`
* Construct file: `r params$ref_file`

## Construct structure

```{r construct, echo=FALSE, message=FALSE, warning=FALSE, fig.height=2}
plot_construct(cur_obj)
```

## Basic Statistics of the sample file

```{r basic_stat, echo=FALSE, message=FALSE, warning=FALSE}
kable(qc_plot(cur_obj$qc, "Basic statistics"))
```


## Sequence quality control {.tabset}

### Per base quality
```{r qc_per_base, echo=FALSE, message=FALSE, warning=FALSE}
qc_plot(cur_obj$qc, "Per base sequence quality")
```

### Per sequence quality
```{r qc_per_quality, echo=FALSE, message=FALSE, warning=FALSE}
qc_plot(cur_obj$qc, "Per sequence quality scores")
```

### Per base N content
```{r qc_n_content, echo=FALSE, message=FALSE, warning=FALSE}
qc_plot(cur_obj$qc, "Per base N content")
```

### Sequence Duplication Levels

```{r qc_length, echo=FALSE, message=FALSE, warning=FALSE}
qc_plot(cur_obj$qc, "Sequence Duplication Levels")
```

## Alignment score distribution

```{r align_score, echo=FALSE, message=FALSE, warning=FALSE}
plot_score_distribution(cur_obj)
```

Applying filter with alignment score `r params$alignment_score_threshold`
``` {r filter, echo=FALSE, message=FALSE, warning=FALSE}
if (!is.null(params$alignment_score_threshold)) {
  cur_obj$aligned_reads <- filter(cur_obj$aligned_reads,score>params$alignment_score_threshold)
  cur_obj$mutation <- filter(cur_obj$mutation,alignment_score>params$alignment_score_threshold)}
```

## Barcode distribution inequality

```{r inequality, echo=FALSE, message=FALSE, warning=FALSE}
plot_lorenz_curve(cur_obj)
```

## Most frequent mutation patterns

```{r patterns, echo=FALSE, message=FALSE, warning=FALSE}
cur_obj$mutation %>% arrange(by=-count) %>% head(10) %>% 
  mutate(target_seq = sapply(.$target_seq, seq_split)) %>% 
  rename(read="target_seq") %>% 
  kable(format="html", escape=FALSE) %>% 
  kable_styling() %>% 
  column_spec(1, monospace = TRUE)
```

## Number of mutations per barcode

```{r mutation_barplot, echo=FALSE, message=FALSE, warning=FALSE}
num_mutation_histogram(cur_obj)
```

## Summary of mutation events

```{r mutation_summary, echo=FALSE, message=FALSE, warning=FALSE}
mutation_type(cur_obj)
```

## Mutation hotspot plots {.tabset}

### Deletions
```{r deletion, echo=FALSE, message=FALSE, warning=FALSE}
plot_deletion_hotspot(cur_obj)
```

### Insertions
```{r insertion, echo=FALSE, message=FALSE, warning=FALSE}
plot_insertion_hotspot(cur_obj)
```

### Mutations
```{r mutation, echo=FALSE, message=FALSE, warning=FALSE}
plot_point_mutation_hotspot(cur_obj)
```

## Extra information

### QC report creation time

```{r report_creation_time, echo=FALSE}
Sys.time()
```

### Running time to generate the report

```{r running_time, echo=FALSE}
toc()
```


### R Session Information

```{r session_info, echo=FALSE, message=FALSE, warning=FALSE}
sessionInfo()
```

```{r save_rds, include=FALSE, message=FALSE, warning=FALSE}
if(is.null(params$traceQC_obj)) {
  saveRDS(cur_obj, file = params$rds_path)}
```

