---
output: 
  html_document:
    toc: true
    toc_float: true

params:
  date: !r Sys.Date()
  set_title: "TraceQC report"
  debug: TRUE
  input_file: !r system.file("extdata", "test_data", "FASTQ", "example.fastq", package="TraceQC")
  ref_file: !r system.file("extdata", "test_data", "ref", "ref.txt", package="TraceQC")
  fastqc_dir: !r tempfile()
  output_dir: !r tempdir()
  ncores: 4
---

---
title: `r params$set_title`
date: `r params$date`
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(TraceQC)
library(fastqcr)
```


```{r data_loading, include=FALSE, warning=FALSE, include=FALSE}
if(!params$debug) {
  fastqc(dirname(params$input_file), qc.dir=params$fastqc_dir)
  fastqc_file <- get_qcpath(params$input_file, params$fastqc_dir)
  cur_obj <- TraceQC(
    input_file = params$input_file,
    ref_file = params$ref_file,
    fastqc_file = fastqc_file,
    ncores = params$ncores
  )
} else {
  data(example_obj)
  cur_obj <- example_obj
}
```

## Construct structure

```{r construct, echo=FALSE, message=FALSE, warning=FALSE, fig.height=2}
plot_construct(cur_obj)
```

## Sequence quality control {.tabset}

### Per base quality
```{r qc_per_base, echo=FALSE, message=FALSE, warning=FALSE}
qc_plot(cur_obj$qc, "Per base sequence quality")
```

### Per sequence quality
```{r qc_per_quality, echo=FALSE, message=FALSE, warning=FALSE}
qc_plot(cur_obj$qc, "Per sequence quality scores")
```

### Per base N content
```{r qc_n_content, echo=FALSE, message=FALSE, warning=FALSE}
qc_plot(cur_obj$qc, "Per base N content")
```

### Sequence Duplication Levels

```{r qc_length, echo=FALSE, message=FALSE, warning=FALSE}
qc_plot(cur_obj$qc, "Sequence Duplication Levels")
```


## Alignment score distribution

```{r align_score, echo=FALSE, message=FALSE, warning=FALSE}
plot_score_distribution(cur_obj)
```

## Barcode distribution inequality

```{r inequality, echo=FALSE, message=FALSE, warning=FALSE}
lorenz_curve(cur_obj)
```


## Number of mutations per barcode

```{r mutation_barplot, echo=FALSE, message=FALSE, warning=FALSE}
num_mutation_histogram(cur_obj)
```

## Summary of mutation events

```{r mutation_summary, echo=FALSE, message=FALSE, warning=FALSE}
mutation_type(cur_obj)
```

## Mutation hotspot plots {.tabset}

### Deletions
```{r deletion, echo=FALSE, message=FALSE, warning=FALSE}
plot_deletion_hotspot(cur_obj)
```

### Insertions
```{r insertion, echo=FALSE, message=FALSE, warning=FALSE}
plot_insertion_hotspot(cur_obj)
```

### Mutations
```{r mutation, echo=FALSE, message=FALSE, warning=FALSE}
plot_point_mutation_hotspot(cur_obj)
```

## QC report creation time

```{r report_creation_time, echo=FALSE}
Sys.time()
```


## R Session Information

```{r session_info, echo=FALSE, message=FALSE, warning=FALSE}
sessionInfo()
```

